---
title: "quokka session 2"
output: html_notebook
---

# Examples of tidyeval and NSE that make their life easier

```{r}
# Nick's example of when NSE is useful.

airquality <- tibble::as_tibble(airquality)

airquality

library(naniar)

airquality %>% add_prop_miss()

# can refer to variables without needing to use "" or data$var

airquality %>% add_prop_miss(Ozone, Solar.R)

# I can also (somehow, magically), take advantage of dplyr::contains and friends
airquality %>% add_prop_miss(dplyr::contains("o"))

airquality %>% add_prop_miss(dplyr::ends_with("y"))

library(dplyr)

airquality %>%
  select(contains("o"))

```

So why `!!!` not just always `!!` ?

- `!!!` (tribang) is explicitly for unquoting `...` or a list of expressions into a list of quosures.

- `!!` is explicitly unquoting just one expression into a quosure

- this name gets value but it's coming from a different place

```{r}
bla <- function(...)

bla(1,4,g,"c")

bla_y <- function(y)

bla(list(1,4,g,"c"))
  
```

# cameron's example


```{r}

predict_ex <- function(...){
  ex_alist <- eval(substitute(alist(...)))
  ex_list <- eval(substitute(list(...)))
  
  return(list(
    alist = ex_alist,
    list = ex_list
  ))
}
str(predict_ex(airquality))


```

And now...using rlang

```{r}
ex_rlang <- function(...){
  
  tidy_alist <- rlang::eval_tidy(rlang::quos(...))
  
  base_alist <- eval(substitute(alist(...)))
  # tidy_data <- rlang::eval_tidy(rlang::UQS(rlang::quos(...)))
  
  tidy_data <- rlang::UQS(rlang::quos(...))
  
  tidy_data_l <- lapply(rlang::quos(...), rlang::eval_tidy)
  
  tidy_data_p <- purrr::map(rlang::quos(...), rlang::eval_tidy)
  
  tidy_data_bare <- rlang::eval_bare(rlang::quos(...))
  
  tidy_data_b <- rlang::eval_tidy(rlang::quos(...), 
                                  env = parent.frame())
  
  base_data <-  eval(substitute(list(...)))
  
  return(list(
    tidy_alist = tidy_alist,
    base_alist = base_alist,
    tidy_data = tidy_data,
    tidy_data_l = tidy_data_l,
    tidy_data_p = tidy_data_p,
    tidy_data_bare = tidy_data_bare,
    tidy_data_b = tidy_data_b,
    base_data = base_data
  ))
  
}

str(ex_rlang(airquality))

library(rlang)


```




```{r}
# standard eval?
plot(airquality$Ozone,
     airquality$Solar.R)
```

```{r}
# non-standard?
with(airquality,
     plot(Ozone,
          Solar.R))

# it evaluates the expression in the environment specified

```

```{r}
# base NSE

# transform
# subset
```


# Questions we have about using NSE / tidyeval in R


# (Jargon) Word(s) of the day


## quote


## unquote

## quosure

