---
title: "Session 4"
date: "2017-09-18, Monday, 3pm"
output: html_document
---

Potential outline for the coming weeks. The next quokka meeting is on the 18th September 

1. Rstats News: "Any news in R that's interesting?"

- Rstudio has launched [an online community](https://community.rstudio.com/) to support tidyverse, shiny, package development, and rstudio related topics:
  - https://blog.rstudio.com/2017/09/14/rstudio-community/
  - https://twitter.com/hadleywickham/status/908337225347280897
  - Kickstarting their 

- Cool blog posts:
  - [Edwin Thoen: how tidy eval builds on base R](https://edwinth.github.io/blog/nse/)
  - [Mara Averick's roundup of tidyeval resources](http://maraaverick.rbind.io/2017/08/tidyeval-resource-roundup/)
  - [RStudio v1.1 - the little things](https://blog.rstudio.com/2017/09/13/rstudio-v1.1---the-little-things/)
  - [Data visualisation for the social sciences](http://socviz.co/)
  - [plotly 4.7.1 on CRAN](https://moderndata.plot.ly/plotly-4-7-1-now-on-cran/)
  - [Discussion/roundup on unifying packages to help users access R repos](https://nashjc.wordpress.com/2017/09/03/unifying-packages-to-help-users-access-r-repositories/)
  - [rOpenSci post about their onboarding process](https://ropensci.org/blog/blog/2017/09/11/software-review-update)
  - [rOpenSci Spelling check package](https://ropensci.org/blog/technotes/2017/09/07/spelling-release)
  - [rOpenSci code review](https://ropensci.org/blog/blog/2017/09/01/nf-softwarereview)
  - Keras R package
  - Tensorflow R package
  - [Markdrive pkg](https://github.com/milesmcbain/markdrive) + fetch script for new data from google drive = awesome.

- R source
  - Changing the C-level representations of objects in R source. E.g., Vectors being marked as sorted, or as a sequence. Big potential for good speedups
  - [Alternative Representations for R Objects](https://svn.r-project.org/R/branches/ALTREP/ALTREP.html)
  
- Any R packages we've released?
  - Roger's `queue` package for queueing abstract data types, to facilitate running certain processes at certain times - powered by the thor package. Parallel processing in the future.
  
- visdat accepted into JOSS

2. Oh God, Help.

 - no-one reported help

3. Reading group: Metaprogramming section of Advanced R

- http://adv-r.hadley.nz/nse.html#capturing-expressions
- Chapter 17.1 discussion:
  - Read through 17.1 and do exercises.
  - Discuss answers and thoughts
  - Discuss future paths (how much and how long to read?)

```{r}

i <- function(x) deparse(quote(x))
g <- function(x) deparse(substitute(x))

i(1:10)
g(1:10)

quote(1+1)
substitute(1+1)
```

```{r}
quote(1+1)
substitute(1+1)
x <- 10
substitute(x)
substitute(1+1)

s <- function(x) substitute(x)
q <- function(x) quote(x)

x
s(y)

q(y)

```

- quote will not try and operate on what it is given
- substitute will try and operate on what it is given (it will substitute in any promises (symbols it can resolve)), and you can specify which place it looks these up - default is the current env.

```{r}
h <- function(...) deparse(substitute(...))
h_l <- function(...) deparse(substitute(list(...)))

h(1:10, "a")
h_l(1:10, "a")

```

```{r}
D(quote(x^2), "x")
```

AS a user, there aren't really many times that you want to use `quote`. Roger made the point that there are two times.

1. The `D` function for symbolic differentiation
2. Passing expressions to `trace()`

Thomas Lumley has an article about this IN 2001!

https://www.r-project.org/doc/Rnews/Rnews_2001-3.pdf


