---
title: "Session-4-answers"
output: html_document
---

Non-standard evaluation: Capturing expressions 

**Question 1**

One important feature of deparse() to be aware of when programming is that it can return multiple strings if the input is too long. For example, the following call produces a vector of length two:

```{r question-1}

f <- function(x) substitute(x)

g <- function(x) deparse(substitute(x))

f(a + b + c + d + e + f + g + h + i + j + k + l + m +
  n + o + p + q + r + s + t + u + v + w + x + y + z)

g(a + b + c + d + e + f + g + h + i + j + k + l + m +
  n + o + p + q + r + s + t + u + v + w + x + y + z)

```

Why does this happen? Carefully read the documentation for ?deparse. Can you write a wrapper around deparse() so that it always returns a single string?

I couldn't set `width.cutoff` to Inf, so I just set it to 500, which is the largest number.

```{r q1-ans}

h <- function(x) deparse(substitute(x), width.cutoff = 500L)

h(a + b + c + d + e + f + g + h + i + j + k + l + m +
  n + o + p + q + r + s + t + u + v + w + x + y + z)

```

# Q2

Why does `as.Date.default()` use `substitute()` and `deparse()`? Why does `pairwise.t.test()` use them? Read the source code.

- `as.Date.default()` uses the `deparse(substitute())` combo so that it can exactly capture the input as a string to put into an error message.

```{r}
as.Date.default("m")
```

- `gettextf` translates an error message into the system language - iff there is a translated error message available. otherwise identical to `sprintf`.

- `pairwise.t.test()` uses them to describe the data input

```{r}

airquality$Month <- factor(airquality$Month, labels = month.abb[5:9])
pw_test <- pairwise.t.test(airquality$Ozone, airquality$Month)

pw_test$data.name
pw_test
```

# Q3

`pairwise.t.test()` assumes that `deparse()` always returns a length one character vector. Can you construct an input that violates this expectation? What happens?

I'm not sure - here is what I tried:

```{r}

airquality$`Month of the year in the english language and entered in today on the 2017-09-18` <- factor(airquality$Month, labels = month.abb[5:9])
pw_test <- pairwise.t.test(airquality$Ozone + airquality$Ozone, 
                           airquality$`Month of the year in the english language and entered in today on the 2017-09-18`)

pw_test
```

# Q4

`f()`, defined above, just calls substitute(). Why can’t we use it to define g()? In other words, what will the following code return? First make a prediction. Then run the code and think about the results.

```{r}

f <- function(x) substitute(x)
g <- function(x) deparse(f(x))

g(1:10)
g(x)
g(x + y ^ 2 / z + exp(a * sin(b)))

```

Because it takes the result of `f(x)` and turns it into a character vector, which at this level, is just `x`!

Why use `deparse` by itself?

to print a formula call as a string, e.g., `y ~ x`.
