---
title: "session-5-chapter-notes"
output: html_document
---

## Chapter 17-18

R allows you to not only access the values of a functions arguments, but the code that was used to compute them. This means that you can evaluate code in non-standard ways, generally speaking meaning that the code used to compute values, or some sort of different context can be used to help evaluate some code.

This gives rise to some really useful features, helping you reduce the amount of typing.

Code is structured as a tree (an Abstract Syntax Tree [AST]), with branches and leaves. The branches are the calls, and the leaves are names and constants.

These trees are generally created from a string, by parsing the code.

The opposite operation from parsing the code is deparsing it.

It is also possible to modify the tree by hand, and insert any R object - which to me seems to indicate that you can override usual lookup rules by inserting certain things into certain parts of the branches of the trees.


### Chapter 18.1 : Structure of expressions

**operations and results**

You can capture code used using `quote`

```{r}
z <- quote(y <- x * 10)
z
```

Which is what is called an *epxression* - an action that can be performed by R.

This is different to a string
```{r}
st <- "y <- x * 10"
```

```{r}
str(z)
str(st)
```

You can represent these expresisons (or ASTs) as a hierarchical tree with `pryr`

```{r}
pryr::ast(y <- x * 10)
```

All possbile expressions are comparised of four pieces:

1. constants ("a", 10, NULL) - length one atomic vectors. Quoting doens't change these.
2. names (or symbols). These represent the name of an object rather than its value.
3. calls - the act of calling a function. Can contains constants, names, other calls
4. pairlists. legacy. Sorta like the named arguments of a function, behaves like a call - is recursive and ca contain constants, names and calls.

`st1` doesn't follow naming conventions when describing objects.

# 18.1.1 Exercises

## Q1

> There’s no existing base function that checks if an element is a valid component of an expression (i.e., it’s a constant, name, call, or pairlist). Implement one by guessing the names of the “is” functions for calls, names, and pairlists.

```{r}
# is.function(mean)

is_constant <- function(x) is.atomic(x)

is_name <- function(x) is.name(x)

is_call <- function(x) is.function(x)

is_pairlist

```


## Q2 

> pryr::ast() uses non-standard evaluation. What’s its escape hatch to standard evaluation?

`call_tree`?

## Q3

> What does the call tree of an if statement with multiple else conditions look like?

```{r}
pryr::ast(
  if(x == 1) "bleep" else if (x == 2) "bloop" else if (x == 3) "bleeeeeeeep"
)
```


## Q4

> Compare ast(x + y %+% z) to ast(x ^ y %+% z). What do they tell you about the precedence of custom infix functions?

```{r}
pryr::ast(x + y %+% z)

pryr:::ast(x ^ y %+% z)
```

```{r}
letters[1:10] %+% chr(1:10)
```


## Q5

> Why can’t an expression contain an atomic vector of length greater than one? Which one of the six types of atomic vector can’t appear in an expression? Why?

raw?

# 18.2 - Names / symbols

`as.name` converts string to name, otherwise use `quote`.

invalid names are surrounded by backticks

- Empty names? I don't get why?

"only useful to programmatically create a function with missing args"

# 18.2.1 Exercises

## Q1 

You can use formals() to both get and set the arguments of a function. Use formals() to modify the following function so that the default value of x is missing and y is 10.

```{r}
g <- function(x = 20, y) {
  x + y
}

formals(g)

formals(g)$x <- quote(expr=)

g

```

## Q2

Write an equivalent to get() using as.name() and eval(). Write an equivalent to assign() using as.name(), substitute(), and eval(). (Don’t worry about the multiple ways of choosing an environment; assume that the user supplies it explicitly.)

# 18.3 Calls

## 18.3 exercises

### Q1

The following two calls look the same, but are actually different:

```{r}

(a <- call("mean", 1:10))

(b <- call("mean", quote(1:10)))

identical(a, b)

```

What’s the difference? Which one should you prefer?

2. Implement a pure R version of do.call().

3. Concatenating a call and an expression with c() creates a list. Implement concat() so that the following code works to combine a call and an additional argument.

```{r}

concat(quote(f), a = 1, b = quote(mean(a)))
#> f(a = 1, b = mean(a))
```


4. Since list()s don’t belong in expressions, we could create a more convenient call constructor that automatically combines lists into the arguments. Implement make_call() so that the following code works.

```{r}

make_call(quote(mean), list(quote(x), na.rm = TRUE))

make_call(quote(mean), quote(x), na.rm = TRUE)

```

5. How does mode<- work? How does it use call()?

6. Read the source for pryr::standardise_call(). How does it work? Why is is.primitive() needed?

7. standardise_call() doesn’t work so well for the following calls. Why?

```{r}

standardise_call(quote(mean(1:10, na.rm = TRUE)))

standardise_call(quote(mean(n = T, 1:10)))

standardise_call(quote(mean(x = 1:10, , TRUE)))
```

8. Read the documentation for pryr::modify_call(). How do you think it works? Read the source code.

9. Use ast() and experimentation to figure out the three arguments in an if() call. Which components are required? What are the arguments to the for() and while() calls?

# 18.4 Pairlists

Pairlists are lists everywhere except funciton args.

