---
title: "Notes from quokka meeting 1"
output: html_notebook
---

When and why to use non standard evaluation?
  
- Passing a formula into lm: 

```{r}

lm(Sepal.Length ~ Sepal.Width + Species, iris)

```

The formula means nothing without the iris dataset, so you cannot evaluate the formula on its own.

It's a way of linking together

data %>% ggplot(aes(var1, var2))

- `lm.fit` - takes a 

# things to know

- Environments and scoping, when + where do things get evaluated in R?
  - what is lazy evaluation?
- what really is an evironment?

So an environment is a collection of symbol value pairs.

```{r}
x <- 1
y <- 3*3
```

So we have x, and y, these are our symbol and value pairs.

- `x <- 1`
- So the left hand side is a symbol, x
- on the RHS is a value, 1

`y <- 3 * 3`
- LHS is still a symbol
- RHS is an _expression_ - the `3*3`. This will be evaluated when you return y UNLESS, you tell R to not to evaluate `3*3`.

```{r}
y <- 3*3
y
```

BUT how do you not evaluate `3*3`

- quote

```{r}
quote(3*3)
```

```{r}
y <- quote(3*3)
y
```


You can also use `delayedAssign()`.

# when are where are things evaluated?

In the console, these are evaluated immediately.

```{r}
3*3
y <- 3*3
```

```{r}

my_return <- function(){
  
  y <- 3*3
  y
  
}

my_return()

```

```{r}

my_return2 <- function(x){
  
  y <- 3*3
  y
  
}

```

These things

```{r}
my_return2(x = 2*2)
my_return2(z*z)
my_return2(stop("dude."))


```

Surprisingly, no errors, but if we try and give x something it cannot assign, we do.

```{r}
my_return2(;)
```

This tells us something about how things are evaluated.
It can't assign `;` to anything, so we get an error.

So the things we put inside a function to give some symbol a value, have to assigned, even if they arent used.

So assignment is not delayed, evaluation is.

So it has to recognize thigns you type, not evaluate them.

`.` is a valid name, so we get no error.

```{r}
my_return2(.)
```

# When do we care about when things are evaluated in functions?

WE really care about the context that things are evaluated in.

This tells us exactly where y, x1, and x2 come from.

`lm(my_data$y ~ my_data$x1 + my_data$x2)`

Here, `lm` is doing somethign special to recognize where they come from

`lm(y ~ x1 + x2, data = my_data)`

And we want want to do something  like the second option because:

1. Easily reusable - you have 5 datasets with the same structure, you can run the same code.


```{r}
xx <- 1

my_print <- function(){
  
  print(xx)
  
}

my_print()

```

```{r}
xx <- 1
my_print <- function(){
  xx <- 2
  toy <- function(){
    xx * 2
  }
  return(toy())
}

my_print()
my_print()

```

So this is really nice, because it means you don't need to 

- what is scoping? What is in-scope? What is out of scope?

```{r}

rlang::quo(group)

example_quo <- function(group){
  
  print(rlang::quo(group))
  
}

example_quo(bla)


```


# next session

- bring in examples of tidyeval and NSE where it makes your life easier
  - "programming with dplyr vignette"
- questions we have about NSE in R
- "Word of the day"
  - submit words, highest wins.
  
